```{r imports}
library(plotly)
library(tidyverse)
library(compmus)
library(tidymodels)
library(ggdendro)
library(heatmaply)
```


---
title: "ATW"
sidebar: atw
format:
  html:
    theme: quartz
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

Released by New West Records on 24-2-2017 <br>
Genres according to database MusicBrainz<br>
- Blues rock
- Psychedelic rock
- Hard rock
- Neo-psychedelica
- Rock<br><br>
Producer: Ben McLeod<br>
Songwriting credits:<br>
- Charles Michael Parks Jr. - Vocals, Bass guitar and Loops<br>
- Jonathan Draper - Rhodes Piano, Organ, Synthesizers and Percussion<br>
- Ben McLeod - Electric Guitar and Acoustic Guitar<br>
- Robby Staebler - Drums, Percussion and Loops<br>
<br>

### Metadata

..
```{r}
alltracks <- read_csv("computational_musicology_alltracks.csv")

alltracks <- alltracks %>%
  rename(duration = `Duration (ms)`)

atw_data <- "ATW"

atw_df <- alltracks %>%
  filter(`Album Name` == "ATW") %>%
  mutate(
    duration_min = duration / 60000,
    duration_label = sprintf(
      "%d:%02d",
      duration %/% 60000,
      (duration %% 60000) %/% 1000
    )
  )

atw_df <- atw_df %>%
  mutate(`Track Name` = factor(`Track Name`, levels = `Track Name`))

ggplot(atw_df, aes(x = duration_min, y = forcats::fct_rev(`Track Name`))) +
  geom_col(fill = "#EB2E84") +
  geom_text(aes(label = duration_label), hjust = -0.1, size = 3) +
  labs(
    title = "Duration per Track",
    x = "Duration (minutes)",
    y = "Track"
  ) +
  theme_minimal() +
  xlim(0, max(atw_df$duration_min) * 1.1)
```
```{r}
alltracks %>%
  filter(`Album Name` == "ATW") %>%
  group_by(`Album Name`) %>%
  mutate(`Track Name` = factor(`Track Name`, levels = rev(unique(`Track Name`)))) %>%
  ungroup() %>%
  ggplot(aes(x = `Track Name`, y = Tempo)) +
  geom_col(fill = "#EB2E84") +
  coord_flip() +
  labs(
    x = "Track",
    y = "Tempo (BPM)",
    title = "Tempo per Track"
  ) +
  theme_minimal()
```

## Clustering and Classification

```{r}
atw_juice <-
  alltracks %>%
  filter(`Album Name` == "ATW") %>%
  mutate(`Track Name` = str_trunc(`Track Name`, 36)) %>%
  recipe(
    `Track Name` ~
      Danceability +
      Energy +
      Loudness +
      Speechiness +
      Acousticness +
      Instrumentalness +
      Liveness +
      Valence +
      Tempo
  ) |>
  step_center(all_predictors()) |>
  step_scale(all_predictors()) |> 
  prep() |>
  juice() |>
  column_to_rownames("Track Name")

atw_dist <- dist(atw_juice, method = "euclidean")

atw_dist |> 
  hclust(method = "complete") |> 
  dendro_data() |>
  ggdendrogram()
```
Fishbelly 86 Onions<br>
Diamond
## Harmony

```{r}
fishbelly <- read_csv("dat/fishbelly.csv")

fishbelly |>
  compmus_wrangle_chroma() |> 
  mutate(pitches = map(pitches, compmus_normalise, "euclidean")) |>
  compmus_gather_chroma() |> 
  ggplot(
    aes(
      x = start + duration / 2,
      width = duration,
      y = pitch_class,
      fill = value
    )
  ) +
  geom_tile() +
  labs(x = "Time (s)", y = NULL, fill = "Magnitude") +
  theme_minimal() +
  scale_fill_viridis_c()
```

```{r}
diamond <- read_csv("dat/diamond.csv")

diamond |>
  compmus_wrangle_chroma() |> 
  mutate(pitches = map(pitches, compmus_normalise, "euclidean")) |>
  compmus_gather_chroma() |> 
  ggplot(
    aes(
      x = start + duration / 2,
      width = duration,
      y = pitch_class,
      fill = value
    )
  ) +
  geom_tile() +
  labs(x = "Time (s)", y = NULL, fill = "Magnitude") +
  theme_minimal() +
  scale_fill_viridis_c()
```


```{r}
circshift <- function(v, n) {
  if (n == 0) v else c(tail(v, n), head(v, -n))
}

#      C     C#    D     Eb    E     F     F#    G     Ab    A     Bb    B
major_chord <-
  c(   1,    0,    0,    0,    1,    0,    0,    1,    0,    0,    0,    0)
minor_chord <-
  c(   1,    0,    0,    1,    0,    0,    0,    1,    0,    0,    0,    0)
seventh_chord <-
  c(   1,    0,    0,    0,    1,    0,    0,    1,    0,    0,    1,    0)

major_key <-
  c(6.35, 2.23, 3.48, 2.33, 4.38, 4.09, 2.52, 5.19, 2.39, 3.66, 2.29, 2.88)
minor_key <-
  c(6.33, 2.68, 3.52, 5.38, 2.60, 3.53, 2.54, 4.75, 3.98, 2.69, 3.34, 3.17)

chord_templates <-
  tribble(
    ~name, ~template,
    "Gb:7", circshift(seventh_chord, 6),
    "Gb:maj", circshift(major_chord, 6),
    "Bb:min", circshift(minor_chord, 10),
    "Db:maj", circshift(major_chord, 1),
    "F:min", circshift(minor_chord, 5),
    "Ab:7", circshift(seventh_chord, 8),
    "Ab:maj", circshift(major_chord, 8),
    "C:min", circshift(minor_chord, 0),
    "Eb:7", circshift(seventh_chord, 3),
    "Eb:maj", circshift(major_chord, 3),
    "G:min", circshift(minor_chord, 7),
    "Bb:7", circshift(seventh_chord, 10),
    "Bb:maj", circshift(major_chord, 10),
    "D:min", circshift(minor_chord, 2),
    "F:7", circshift(seventh_chord, 5),
    "F:maj", circshift(major_chord, 5),
    "A:min", circshift(minor_chord, 9),
    "C:7", circshift(seventh_chord, 0),
    "C:maj", circshift(major_chord, 0),
    "E:min", circshift(minor_chord, 4),
    "G:7", circshift(seventh_chord, 7),
    "G:maj", circshift(major_chord, 7),
    "B:min", circshift(minor_chord, 11),
    "D:7", circshift(seventh_chord, 2),
    "D:maj", circshift(major_chord, 2),
    "F#:min", circshift(minor_chord, 6),
    "A:7", circshift(seventh_chord, 9),
    "A:maj", circshift(major_chord, 9),
    "C#:min", circshift(minor_chord, 1),
    "E:7", circshift(seventh_chord, 4),
    "E:maj", circshift(major_chord, 4),
    "G#:min", circshift(minor_chord, 8),
    "B:7", circshift(seventh_chord, 11),
    "B:maj", circshift(major_chord, 11),
    "D#:min", circshift(minor_chord, 3)
  )

key_templates <-
  tribble(
    ~name, ~template,
    "Gb:maj", circshift(major_key, 6),
    "Bb:min", circshift(minor_key, 10),
    "Db:maj", circshift(major_key, 1),
    "F:min", circshift(minor_key, 5),
    "Ab:maj", circshift(major_key, 8),
    "C:min", circshift(minor_key, 0),
    "Eb:maj", circshift(major_key, 3),
    "G:min", circshift(minor_key, 7),
    "Bb:maj", circshift(major_key, 10),
    "D:min", circshift(minor_key, 2),
    "F:maj", circshift(major_key, 5),
    "A:min", circshift(minor_key, 9),
    "C:maj", circshift(major_key, 0),
    "E:min", circshift(minor_key, 4),
    "G:maj", circshift(major_key, 7),
    "B:min", circshift(minor_key, 11),
    "D:maj", circshift(major_key, 2),
    "F#:min", circshift(minor_key, 6),
    "A:maj", circshift(major_key, 9),
    "C#:min", circshift(minor_key, 1),
    "E:maj", circshift(major_key, 4),
    "G#:min", circshift(minor_key, 8),
    "B:maj", circshift(major_key, 11),
    "D#:min", circshift(minor_key, 3)
  )
```
```{r}
fishbelly |> 
  compmus_wrangle_chroma() |> 
  filter(row_number() %% 50L == 0L) |> 
  compmus_match_pitch_template(
    key_templates,         # Change to chord_templates if desired
    method = "euclidean",  # Try different distance metrics
    norm = "manhattan"     # Try different norms
  ) |>
  ggplot(
    aes(x = start + duration / 2, width = 50 * duration, y = name, fill = d)
  ) +
  geom_tile() +
  scale_fill_viridis_c(guide = "none") +
  theme_minimal() +
  labs(x = "Time (s)", y = "")
```

```{r}
diamond |> 
  compmus_wrangle_chroma() |> 
  filter(row_number() %% 50L == 0L) |> 
  compmus_match_pitch_template(
    key_templates,         # Change to chord_templates if desired
    method = "euclidean",  # Try different distance metrics
    norm = "manhattan"     # Try different norms
  ) |>
  ggplot(
    aes(x = start + duration / 2, width = 50 * duration, y = name, fill = d)
  ) +
  geom_tile() +
  scale_fill_viridis_c(guide = "none") +
  theme_minimal() +
  labs(x = "Time (s)", y = "")
```


```{r}
fishbelly |> 
  compmus_wrangle_chroma() |> 
  filter(row_number() %% 50L == 0L) |> 
  compmus_match_pitch_template(
    chord_templates,         # Change to chord_templates if desired
    method = "euclidean",  # Try different distance metrics
    norm = "manhattan"     # Try different norms
  ) |>
  ggplot(
    aes(x = start + duration / 2, width = 50 * duration, y = name, fill = d)
  ) +
  geom_tile() +
  scale_fill_viridis_c(guide = "none") +
  theme_minimal() +
  labs(x = "Time (s)", y = "")
```
```{r}
diamond |> 
  compmus_wrangle_chroma() |> 
  filter(row_number() %% 50L == 0L) |> 
  compmus_match_pitch_template(
    chord_templates,         # Change to chord_templates if desired
    method = "euclidean",  # Try different distance metrics
    norm = "manhattan"     # Try different norms
  ) |>
  ggplot(
    aes(x = start + duration / 2, width = 50 * duration, y = name, fill = d)
  ) +
  geom_tile() +
  scale_fill_viridis_c(guide = "none") +
  theme_minimal() +
  labs(x = "Time (s)", y = "")
```
## Rhythm and Tempo



## Timbre



# Structure


