
```{r imports}
library(plotly)
library(tidyverse)
library(compmus)
```

```{r}
fourtyonedft <- read_csv("./dat/41dft.csv")
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

---
title: "Portfolio"
author: "Merijn Dekker"
theme: minty
format:
  dashboard:
    orientation: columns
---





# Introduction page

## Column


### Row {height=20%}
::: {.card}
This is the main page of my portfolio. 

:::

### Row {height=80%}

::: {.card title="work in progress"}
.

:::



## Column
### Row {height=20%}

::: {.card title="work in progress"}


:::

### Row {.tabset}

::: {.card title="work in progress"}
.

:::



## Column

### Row {.tabset}

::: {.card title="work in progress"}
.

:::

# Week 11

## Column

### Row {height=100%}

::: {.card title="Homework week 11"}
Shown on the right side is a dft tempogram of a track called 41 from the album Nothing as the Ideal by All Them Witches. This track is mostly stated to be around 120 bpm by multiple online sources. What's interesting about this song is the fact that the drums play a half-time feel, meaning the kick is played on the 1 of the beat and the snare on the 3. While the drum is playing half-time, the guitar and bass are playing eighth notes. This lead me to think that sonic visualiser would have problems analysing this piece of music. some value around 120 is visible in the plot, but the double value is far more noticeable. This makes me think that the bass and guitar parts are tracked by sonic visualiser to generate a bpm. 
:::

## Column

### Row {height=100%}

::: {.card title=}
```{r plot-chunk, echo=FALSE}
#| title: All them witches - 41 DFT
fourtyonedft |> 
  pivot_longer(-TIME, names_to = "tempo") |> 
  mutate(tempo = as.numeric(tempo)) |> 
  ggplot(aes(x = TIME, y = tempo, fill = value)) +
  geom_raster() +
  scale_fill_viridis_c(guide = "none") +
  labs(x = "Time (s)", y = "Tempo (BPM)") +
  theme_classic()
```
:::