```{r imports}
library(plotly)
library(tidyverse)
library(compmus)
library(tidymodels)
library(ggdendro)
library(heatmaply)
```
```{r}
fourtyonedft<- read_csv("./dat/41dft.csv")
alltracks <- read_csv("./dat/computational_musicology_alltracks.csv") 
```

---
title: "Nothing as the Ideal"
format:
  html:
    theme: quartz
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Tracklist

- Song 1
- Song 2
- Song 3

# Review

Your review content here.

### Row {height=100%}

::: {.card title="Homework week 11"}
Shown on the right side is a dft tempogram of a track called 41 from the album Nothing as the Ideal by All Them Witches. This track is mostly stated to be around 120 bpm by multiple online sources. What's interesting about this song is the fact that the drums play a half-time feel, meaning the kick is played on the 1 of the beat and the snare on the 3. While the drum is playing half-time, the guitar and bass are playing eighth notes. This lead me to think that sonic visualiser would have problems analysing this piece of music. some value around 120 is visible in the plot, but the double value is far more noticeable. This makes me think that the bass and guitar parts are tracked by sonic visualiser to generate a bpm. 
:::

## Column

### Row {height=100%}

::: {.card title=}
```{r plot-chunk, echo=FALSE}
#| title: All them witches - 41 DFT
fourtyonedft |> 
  pivot_longer(-TIME, names_to = "tempo") |> 
  mutate(tempo = as.numeric(tempo)) |> 
  ggplot(aes(x = TIME, y = tempo, fill = value)) +
  geom_raster() +
  scale_fill_viridis_c(guide = "none") +
  labs(x = "Time (s)", y = "Tempo (BPM)") +
  theme_classic()
```
:::




## Column {width=50%}

### Row

::: {card}
```{r, echo=FALSE}
alltracks_juice <-
  recipe(
    `Track Name` ~
      Danceability +
      Energy +
      Loudness +
      Speechiness +
      Acousticness +
      Instrumentalness +
      Liveness +
      Valence +
      Tempo +
      `Duration (ms)`,
    data = alltracks
  ) |>
  step_center(all_predictors()) |>
  step_scale(all_predictors()) |> 
  prep(alltracks |> mutate(`Track Name` = str_trunc(`Track Name`, 36))) |>
  juice() |>
  column_to_rownames("Track Name")
```
```{r, echo=FALSE}
alltracks_dist <- dist(alltracks_juice, method = "euclidean")
```
```{r, echo=FALSE}
alltracks_dist |> 
  hclust(method = "complete") |> # Try single, average, and complete.
  dendro_data() |>
  ggdendrogram()
```
:::

::: {card}

```{r, echo=FALSE}
alltracks2_juice <-
  recipe(
    `Track Name` ~
      Energy +
      Loudness,
    data = alltracks
  ) |>
  step_center(all_predictors()) |>
  step_scale(all_predictors()) |> 
  prep(alltracks |> mutate(`Track Name` = str_trunc(`Track Name`, 36))) |>
  juice() |>
  column_to_rownames("Track Name")
```
```{r, echo=FALSE}
alltracks2_dist <- dist(alltracks2_juice, method = "euclidean")
```
```{r, echo=FALSE}
alltracks2_dist |> 
  hclust(method = "complete") |> # Try single, average, and complete.
  dendro_data() |>
  ggdendrogram()
```

:::

## Column

### Row {height=50%}

The first dendrogram to the left is made up of all songs used in the corpus. All variables as extracted from exportify are used. These are: danceability, energy, loudness, speechiness, acousticness, instrumentalness, liveness, valence and tempo. The clusters seem to make sense to some extent. clusters like the 2nd, 3rd, 4th, 5th and 6th track are quite similar in ways. They are all higher energy, mostly distorted sounding tracks. These kind of variables can be clustered even better.

### Row{height=50%}

The second dendrogram is also made up of all songs used in the corpus, but this time only energy and loudness are used. This makes the clusters as seen in the dendrogram to be more specific and therefore more logical to read and it is easier to make conclusions while listening. The interesting part about this dendogram is the fact that all clusters seem to have tracks from different albums, concluding that, with only these dendrograms, there is no reason to believe that the albums differ in energy and loudness level.
